\section{Differential Geometry on Manifolds}
This is a very brief summary of choice results in differential geometry. For details, please consult my summary of SI2360 Analytical Mechanics and Classical Field Theory.

\paragraph{Manifolds}
A manifold is a set which is locally isomorphic to $\R^{n}$. We will take this to mean that we can locally impose coordinates $\chi^{a}$ on the manifold.

More formally, a manifold is described by a number of sets $U_{i}\subset\R^{n}$ called charts. To each chart belongs a set of coordinate functions $\chi_{i}$ which map from a subset $M_{i}\subset M$ to $U_{i}$ such that $\chi_{i}$ is a smooth bijection. A set of charts such that every point $p\in M$ is found in at least one chart is called an atlas.

\paragraph{Tangent Vectors}
Tangent vectors describe how scalar fields change with displacement along a curve. In Euclidean space the tangent basis was composed of derivatives with respect to the set of coordinates. In general curved spaces, we define
\begin{align*}
	\tb{a} = \del{a}{}.
\end{align*}
Derivatives are linear operators, so at least the set of tangent bases span some vector space and it makes sense to call a derivative a vector. A general tangent vector is now
\begin{align*}
	X = X^{a}\tb{a} = X^{a}\del{a}{}.
\end{align*}
These live in the tangent space $\ts{p}{M}$ of the manifold $M$ at the point $p$.

To get more of a sense of how this can be related to vectors, consider the directional derivative
\begin{align*}
	\grad_{\vb{n}} = \vb{n}\cdot\grad = n^{a}\del{a}{}.
\end{align*}
When applied to Euclidean space, there is a direct correspondence between $\vb{n}$ and the directional derivative, as $\grad_{\vb{n}}{\vb{x}} = \vb{n}$. For more general manifolds, tangent vectors are defined to be directional derivatives. Note that this definition carries with it the same dependence on position as was previously warned about.

Tangent vectors transform according to
\begin{align*}
	X^{a}\del{a}{} = X^{a}\del{a}{(\chi^{\prime})^{b}}\del[\prime]{b}{},
\end{align*}
implying the transformation rule
\begin{align*}
	(X^{\prime})^{a} = \del{b}{(\chi^{\prime})^{a}}X^{b},
\end{align*}
which is the same as the transformation rule for contravariant vector components in Euclidean space.

\paragraph{Dual Vectors}
To define dual vectors, we first introduce the dual space as the set of all linear operations from the tangent space to real numbers. This is also a vector space. The basis for the space is defined such that
\begin{align*}
	\db{a}(\del{b}{}) = \kdelta{b}{a}.
\end{align*}

In Euclidean space the dual basis was constructed from the gradient. The only concept here that carries over to manifolds is a definition based on small changes in the coordinates. More specifically, for any smooth scalar field $f$ we define a dual vector field according to
\begin{align*}
	df(X) = Xf = X^{a}\del{a}{f}
\end{align*}
and call it the differential. This has a similar structure to an inner product if the dual vector field has components $df_{a} = \del{a}{f}$. These components correspond to those of the gradient in Euclidean space. The basis we desire is $\db{a} = d\chi^{a}$. These live in the dual space $\ds{p}{M}$ of the manifold $M$ at the point $p$.

The dual basis satisfies satisfies
\begin{align*}
	d\chi^{a}(\del{b}{}) = \del{b}{\chi^{a}} = \kdelta{b}{a},
\end{align*}
as expected. Using this, we obtain
\begin{align*}
	df = (\del{a}{f})d\chi^{a},
\end{align*}
which at least looks like the differential of a function.

The components transform according to
\begin{align*}
	\del{a}{f} = \del[\prime]{b}{f}\del{a}{(\chi^{\prime})^{b}},
\end{align*}
which is the transformation rule for covariant vector components.

\paragraph{Tensors}
Having identified a basis for the tangent and dual spaces, we may now construct tensors similarly to what we have previously done. Note now that as the tangent and dual vectors belong to different vector spaces, the notion of type $(n, m)$ tensors is more clear. This also explains why we needed to be careful with indices being up or down when studying Euclidean space, as the difference is huge for manifolds.

\paragraph{Flow of Vector Fields}
The tangent bundle of a manifold is defined as $TM = \bigcup\limits_{p}\ts{p}{M}$. A vector field is a map $X: M\to\tbun{M}$ such that $X(p)\in\ts{p}{M}$. Given this, we may define the flow of a vector field as a collection of curves $\gamma_{X}$ which given some starting point $p$ satisfy
\begin{align*}
	\deval{\gamma_{X}}{\tau}{p, s} = \eval{X}_{\gamma_{X}(p, s)}.
\end{align*}
We may for a fixed $s$ define the function $\gamma_{sX}(p) = \gamma_{X}(p, s)$, which maps $M$ to itself.

\paragraph{Pushforwards and Pullbacks}
Consider some function $f$ which maps a manifold $M_{1}$ to another manifold $M_{2}$, as well as a function $g: M_{2}\to\R$. We then define the pullback of $g$ to $M_{1}$ by $f$ as $\pub{f}{g} = g\circ f$. We also define the pushforward of a vector $V\in\ts{p}{M_{1}}$ as $(\puf{f}{V})\phi = V(\pub{f}{\phi})$.

\paragraph{Tangents and the Pushforward}
$f$ maps the cooordinates $\chi^{a}$ of $M_{1}$ to the coordinates $\eta^{\mu}$ of $M_{2}$. By definition we have
\begin{align*}
	(\puf{f}{V})\phi &= V(\pub{f}{\phi}) \\
	&= V^{a}\del{a}{(\phi\circ f)} \\
	&= V^{a}\del{\mu}{\phi}\del{a}{\eta^{\mu}},
\end{align*}
meaning $\puf{f}{V} = V^{a}\del{a}{\eta^{\mu}}\del{\mu}{}$.

How do we interpret this? Consider some curve $\gamma$ in $M_{1}$ which is mapped to a curve $\alpha$ $M_{2}$ by $f$. If $V$ is the tangent of $\gamma$ at some particular point, we have
\begin{align*}
	\dot{\alpha} = \dot{\eta^{\mu}}\del{\mu}{} = \del{a}{\eta^{\mu}}\dot{\chi^{a}}\del{\mu}{} = \del{a}{\eta^{\mu}}V^{a}\del{\mu}{},
\end{align*}
meaning that the pushforward of a tangent by $f$ is the tangent of the curve produced by $f$.

\paragraph{The Pullback of Tensors}
We can now define the pullback of a $(0, m)$ tensor on $M_{2}$ according to
\begin{align*}
	\pub{f}{\omega}(V_{1}, \dots, V_{m}) = \omega(\puf{f}{V_{1}}, \dots, \puf{f}{V_{m}}).
\end{align*}
If $f$ is a bijection we may also define the more general pullback of a $(n, m)$ tensor on $M_{2}$ as
\begin{align*}
	\pub{f}{T}(V_{1}, \dots, V_{m}, \omega_{1}, \dots, \omega_{n}) = T(\puf{f}{V_{1}}, \dots, \puf{f}{V_{m}}, \pub{(f^{-1})}{\omega_{1}}, \dots, \pub{(f^{-1})}{\omega_{n}}).
\end{align*}

\paragraph{The Lie Derivative}
For a tensor field $T$ we define the Lie derivative in the $X$-direction as
\begin{align*}
	\lied{X}{T} = \lim\limits_{\varepsilon\to 0}\frac{1}{\varepsilon}\left(\pub{\gamma_{\varepsilon X}}{T} - T\right).
\end{align*}

\paragraph{An Expression for the Lie Derivative}
For a general tensor field we have
\begin{align*}
	\tensor*{(\lied{X}{T})}{^{a_{1}\dots a_{n}}_{b_{1}\dots b_{m}}} &= X^{a}\del{a}{\tensor*{T}{^{a_{1}\dots a_{n}}_{b_{1}\dots b_{m}}}} - \sum\limits_{i = 1}^{n}\tensor*{T}{^{a_{1}\dots a_{i - 1}aa_{i + 1}\dots a_{n}}_{b_{1}\dots b_{m}}}\del{a}{X^{a_{i}}} + \sum\limits_{j = 1}^{m}\tensor*{T}{^{a_{1}\dots a_{n}}_{b_{1}\dots b_{i - 1}ab_{i + 1}\dots b_{m}}}\del{b_{j}}{X^{a}}.
\end{align*}

\paragraph{Connections}
A connection is an operator on a tensor space that satisfies the following:
\begin{itemize}
	\item $\dcov{X}{f} = Xf = X^{a}\del{a}{f}$ for a scalar field $f$.
	\item $\dcov{X + Y}{T} = \dcov{X}{T} + \dcov{Y}{T}$.
	\item $\dcov{fX}{T} = f\dcov{X}{T}$.
	\item $\dcov{X}{(TS)} = (\dcov{X}{T})S + T\dcov{X}{S}$.
\end{itemize}

\paragraph{Connections on Manifolds}
On a manifold, a connection is specified by choosing $n$ independent vectors $X_{i}$ and defining
\begin{align*}
	\dcov{X_{i}}{X_{j}} = \chris{k}{i}{j}X_{k},
\end{align*}
where the expansion coefficients are called connection coefficients or Christoffel symbols. There is no unique way to do this, as the connection then depends on the choice of vectors.

\paragraph{The Connection of a Tensor Field}
Specify the connection according to $\dcov{\del{a}{}}{\del{b}{}} = \chris{c}{a}{b}\del{c}{}$. We then have
\begin{align*}
	\tensor*{(\dcov{X}{T})}{^{a_{1}\dots a_{n}}_{b_{1}\dots b_{m}}} &= X^{a}\left(\del{a}{\tensor*{T}{^{a_{1}\dots a_{n}}_{b_{1}\dots b_{m}}}} + \sum\limits_{i = 1}^{n}\chris{a_{i}}{a}{b}\tensor*{T}{^{a_{1}\dots a_{i - 1}ba_{i + 1}\dots a_{n}}_{b_{1}\dots b_{m}}} - \sum\limits_{j = 1}^{m}\chris{b}{a}{b_{j}}\tensor*{T}{^{a_{1}\dots a_{n}}_{b_{1}\dots b_{j - 1}bb_{j + 1}\dots b_{m}}}\right).
\end{align*}

\paragraph{The Difference Between Two Connections}
Given two different connection $\dcov{}{}$ and $\square$ with connection coefficients $\chris{}{}{}$ and $C$ we have
\begin{align*}
	(\dcov{a}{X} - \square_{a}X)^{b} = \del{a}{X^{b}} + \chris{b}{a}{c}X^{c} - (\del{a}{X^{b}} + C^{b}_{ac}X^{c}) = (\chris{b}{a}{c} - C^{b}_{ac})X^{c},
\end{align*}
and by the tensor quotient rule, the difference in the connection coefficients must transform as a tensor.

\paragraph{Parallel Transport}
A vector $X$ is termed parallel if $\dcov{a}{X} = 0$. This defines $n^{2}$ equations for the $n$ components of $X$, meaning that the system is overdetermined, and generally has no solution on a manifold. We may, however, define $X$ to be parallel along a curve $\gamma$ if
\begin{align*}
	\dcov{\dot{\gamma}}{X} = 0.
\end{align*}
This allows us to define the parallel transport as the vector field that solves the above equation with the vector $X$ as its initial condition. This defines $n$ equations for the $n$ components, and the system is solvable.

In particular, using the properties of the connection we find
\begin{align*}
	\dcov{\dot{\gamma}}{X} &= \dcov{\dot{\chi}^{a}\del{a}{}}{X^{c}\del{c}{}} \\
	&= \dot{\chi}^{a}\dcov{a}{X^{c}\del{c}{}} \\
	&= \dot{\chi}^{a}((\dcov{a}{X^{c}})\del{c}{} + X^{c}\dcov{a}{\del{c}{}}) \\
	&= \dot{\chi}^{a}(\del{a}{X^{b}} + X^{c}\chris{b}{a}{c})\del{b}{}.
\end{align*}

\paragraph{Geodesics and the Geodesic Equation}
A geodesic is defined as a curve with a tangent vector that is parallel along itself.

By definition a geodesic satisfies
\begin{align*}
	\dcov{\dot{\gamma}}{\dot{\gamma}} = \dot{\chi}^{a}(\del{a}{\dot{\chi}^{b}} + \dot{\chi}^{c}\chris{b}{a}{c})\del{b}{} = (\ddot{\chi}^{b} + \dot{\chi}^{a}\dot{\chi}^{c}\chris{b}{a}{c})\del{b}{} = 0,
\end{align*}
and thus
\begin{align*}
	\ddot{\chi}^{b} + \dot{\chi}^{a}\dot{\chi}^{c}\chris{b}{a}{c} = 0.
\end{align*}
This is the geodesic equation. Given a starting point and a tangent vector, it is solvable.

\paragraph{Torsion}
The torsion tensor is a $(1, 2)$ tensor defined as
\begin{align*}
	T(X, Y) = \dcov{X}{Y} - \dcov{Y}{X} - \comm{X}{Y}.
\end{align*}
To find its components, we note that
\begin{align*}
	T_{ab} = T(\del{a}{}, \del{b}{}) &= \dcov{a}{\del{b}{}} - \dcov{b}{\del{a}{}} - \comm{\del{a}{}}{\del{b}{}} \\
	&= \chris{c}{a}{b}\del{c}{} - \chris{c}{b}{a}\del{c}{} - (\del{a}{\del{b}{}} - \del{b}{\del{a}{}}) \\
	&= (\chris{c}{a}{b} - \chris{c}{b}{a})\del{c}{},
\end{align*}
implying
\begin{align*}
	T_{ab}^{c} &= \chris{c}{a}{b} - \chris{c}{b}{a}.
\end{align*}

\paragraph{Curvature}
Consider some vector $Z$ parallel transported along a small closed loop. The parallel transport is linear, so the result of this process must be connected to some $(1, 1)$ tensor. Supposing that the loop is spanned by $X$ and $Y$, we have
\begin{align*}
	Z^{\prime} - Z = R(X, Y)Z = \dcov{X}{\dcov{Y}{Z}} - \dcov{Y}{\dcov{X}{Z}} - \dcov{\comm{X}{Y}}{Z}.
\end{align*}
We define $R(X, Y)Z$ as the Riemann curvature tensor. It is a $(1, 3)$ tensor. Its components are defined by
\begin{align*}
	R(\del{a}{}, \del{b}{})\del{c}{} &= \tensor{R}{^{d}_{cab}}\del{d}{} \\
	&= \dcov{a}{\dcov{b}{\del{c}{}}} - \dcov{b}{\dcov{a}{\del{c}{}}} \\
	&= \dcov{a}{\chris{f}{b}{c}\del{f}{}} - \dcov{b}{\chris{f}{a}{c}\del{f}{}} \\
	&= (\dcov{a}{\chris{f}{b}{c}})\del{f}{} + \chris{f}{b}{c}\dcov{a}{\del{f}{}} - (\dcov{b}{\chris{f}{a}{c}})\del{f}{} - \chris{f}{a}{c}\dcov{b}{\del{f}{}} \\
	&= (\del{a}{\chris{d}{b}{c}} + \chris{f}{b}{c}\chris{d}{a}{f} - \del{b}{\chris{d}{a}{c}} - \chris{f}{a}{c}\chris{d}{b}{f})\del{d}{}, 
\end{align*}
and thus
\begin{align*}
	\tensor{R}{^{d}_{cab}} = \del{a}{\chris{d}{b}{c}} - \del{b}{\chris{d}{a}{c}} + \chris{f}{b}{c}\chris{d}{a}{f} - \chris{f}{a}{c}\chris{d}{b}{f}.
\end{align*}
Note the placements of the indices.

\paragraph{The Metric Tensor}
The metric tensor will be taken as the $(0, 2)$ tensor that defines inner products on manifolds. The inner product, and therefore also the metric tensor, is a map from $\ts{p}{M}\times\ts{p}{M}$ that is symmetric and positive definite. Using this we may extend more of the previously performed work, for instance on curve length.

\paragraph{Metric Compatibility}
A connection is metric compatible if $\dcov{X}{g} = 0$ for all vectors $X$.

\paragraph{The Levi-Civita Connection}
For any manifold with some metric there exists a unique connection that is both metric compatible and torsion free. This connection is termed the Levi-Civita connection.

\paragraph{Curves of Minimal Length}
As the metric defines length, we define the curve length as
\begin{align*}
	l_{\gamma} = \integ{\gamma}{}{s}{} = \integ{0}{1}{t}{\sqrt{g_{ab}\dot{\chi}^{a}\dot{\chi}^{b}}}.
\end{align*}
Defining $\sqrt{\lag} = g_{ab}\dot{\chi}^{a}\dot{\chi}^{b}$, the curve that minimizes the distance between the start and end points satisfies
\begin{align*}
	\del{a}{\sqrt{\lag}} - \dv{t}\pdv{\sqrt{\lag}}{\dot{\chi}^{a}} = \frac{1}{2\sqrt{\lag}}\left(\del{a}{\lag} - \sqrt{\lag}\dv{t}\left(\frac{1}{\sqrt{\lag}}\pdv{\lag}{\dot{\chi}^{a}}\right)\right) = 0.
\end{align*}
One can always choose a parametrization such that $\sqrt{\lag} = 1$ (the arc length parametrization is one example), yielding
\begin{align*}
	\frac{1}{2\sqrt{\lag}}\left(\del{a}{\lag} - \dv{t}\pdv{\lag}{\dot{\chi}^{a}}\right) = 0,
\end{align*}
which is equivalent to extremizing the integral of $\lag$. In terms of the coordinate functions we thus have
\begin{align*}
	\del{a}{g_{bc}}\dot{\chi}^{b}\dot{\chi}^{c} - \dv{t}\pdv{\lag}{\dot{\chi}^{a}} = \del{a}{g_{bc}}\dot{\chi}^{b}\dot{\chi}^{c} - \dv{t}(2g_{ab}\dot{\chi}^{b}) = \del{a}{g_{bc}}\dot{\chi}^{b}\dot{\chi}^{c} - 2g_{ab}\ddot{\chi}^{b} - 2\del{c}{g_{ab}}\dot{\chi}^{b}\dot{\chi}^{c} = 0.
\end{align*}
Multiplying by $-\frac{1}{2}g^{da}$ we find
\begin{align*}
	g^{da}g_{ab}\ddot{\chi}^{b} - \frac{1}{2}g^{da}\del{a}{g_{bc}}\dot{\chi}^{b}\dot{\chi}^{c} + g^{da}\del{c}{g_{ab}}\dot{\chi}^{b}\dot{\chi}^{c} = \ddot{\chi}^{d} + \frac{1}{2}g^{da}(2\del{c}{g_{ab}} - \del{a}{g_{bc}})\dot{\chi}^{b}\dot{\chi}^{c} = 0.
\end{align*}
Renaming indices for convenience we find
\begin{align*}
	\ddot{\chi}^{b} + \frac{1}{2}g^{bd}(2\del{c}{g_{da}} - \del{d}{g_{ac}})\dot{\chi}^{a}\dot{\chi}^{c} = 0.
\end{align*}

\paragraph{Geodesics and Minimum-Length Curves}
Geodesics and curves of minimal length coincide if
\begin{align*}
	\chris{b}{a}{c} = \frac{1}{2}g^{bd}(2\del{c}{g_{da}} - \del{d}{g_{ac}}).
\end{align*}
As the above identification is done based on a quantity that is symmetric in the lower indices, we cannot find any information about the antisymmetric part of the connection coefficients from this.

\paragraph{The Levi-Civita Connection and Geodesics}
The connection coefficients (or Christoffel symbols) defined by the Levi-Civita connection are symmetric due to the torsion being zero. This implies
\begin{align*}
	\chris{d}{a}{b} = \frac{1}{2}g^{dc}(\del{b}{g_{ac}} + \del{a}{g_{cb}} - \del{c}{g_{ab}}).
\end{align*}

\paragraph{The Induced Metric}
Given some immersion $f$ of $M_{1}$ into $M_{2}$ and supposing that the metric $g$ exists on $M_{2}$, this induces a metric $\tilde{g} = \pub{f}{g}$ on $M_{1}$.

\paragraph{Components of the Induced Metric}
Suppose that there is an immersion $f: \chi^{a}\to\eta^{\mu}$ of one manifold into another, and that the metric is $g$ in the outer manifold. By definition the induced metric satisfies $\tilde{g}(U, V) = \pub{f}{g}(U, V) = g(\puf{f}{U}, \puf{f}{V})$, implying
\begin{align*}
	\tilde{g}_{ab}U^{a}V^{b} = g_{\mu\nu}U^{a}\del{a}{\eta^{\mu}}V^{b}\del{b}{\eta^{\nu}},
\end{align*}
and as this is true for any pair of vectors we recognize
\begin{align*}
	\tilde{g}_{ab} = g_{\mu\nu}\del{a}{\eta^{\mu}}\del{b}{\eta^{\nu}}.
\end{align*}

\paragraph{Curvature and the Metric}
Using the Levi-Civita connection, we may then introduce the contravariant curvature components
\begin{align*}
	R_{abcd} &= \frac{1}{2}\left(\del{a}{\del{d}{g_{bc}}} + \del{b}{\del{c}{g_{ad}}} - \del{a}{\del{c}{g_{bd}}} - \del{b}{\del{d}{g_{ac}}}\right) + g_{fh}(\chris{f}{b}{c}\chris{h}{a}{d} - \chris{f}{b}{d}\chris{h}{a}{c}).
\end{align*}
We find $R_{abcd} = R_{cdab} = -R_{abdc} = -R_{bacd}$. In addition, the curvature satisfies the Bianchi identity $R(X, Y)Z + R(Y, Z)X + R(Z, X)Y = 0$, implying $R_{abcd} + R_{acdb} + R_{adbc} = 0$, meaning that the total number of independent components is $\frac{1}{12}n^{2}(n^{2} - 1)$.

\paragraph{Killing Fields}
$K$ is a Killing field if $\lied{K}{g} = 0$.

\paragraph{The Lie Derivative with Killing Fields}
Let $K$ be a Killing field. We then obtain
\begin{align*}
	\lied{K}{g_{ab}} &= \dcov{b}{K_{a}} + \dcov{a}{K_{b}} = 0,
\end{align*}
and all Killing fields must satisfy this relation.

\paragraph{The Ricci Tensor}
The Ricci tensor is defined as $R_{ab} = \tensor{R}{^{c}_{acb}}$. Its components are
\begin{align*}
	R_{ab} = \del{c}{\chris{c}{b}{a}} - \del{b}{\chris{c}{c}{a}} + \chris{f}{b}{a}\chris{c}{c}{f} - \chris{f}{c}{a}\chris{c}{b}{f} .
\end{align*}

\paragraph{The Ricci Scalar}
The Ricci scalar is defined as the trace of the Ricci scalar: $\mathcal{R} = g^{ab}R_{ab} = g^{ab}\tensor{R}{^{c}_{acb}}$.

\paragraph{The Einstein Tensor}
The Einstein tensor is defined as $G_{ab} = R_{ab} - \frac{1}{2}g_{ab}\mathcal{R}$.

\paragraph{Differential Forms}
The set of $p$-forms, or differential forms, is the set of $(0, p)$ tensors that are completely antisymmetric. They are constructed using the wedge product, defined as
\begin{align*}
	\bigwedge\limits_{k = 1}^{p}d\chi^{a_{k}} = \sum\limits_{\sigma\in S_{p}}\text{sgn}(\sigma)\bigotimes_{k = 1}^{p}d\chi^{a_{\sigma(k)}}.
\end{align*}
Here $S_{p}$ is the set of permutations of $p$ elements. There exists
\begin{align*}
	n_{p}^{N} = {N\choose k}
\end{align*}
basis elements. We note that the wedge product is antisymmetric under the exchange of two basis elements. Hence, once an ordering of indices has been chosen, any permutation will simply create a linearly dependent map.

Consider now some antisymmetric tensor $\omega$. Introducing the antisymmetrizer
\begin{align*}
	\bigotimes_{k = 1}^{p}d\chi^{[a_{\sigma(k)}]} = \frac{1}{p!}\sum\limits_{\sigma\in S_{p}}\text{sgn}(\sigma)\bigotimes_{k = 1}^{p}d\chi^{a_{\sigma(k)}},
\end{align*}
the symmetry yields
\begin{align*}
	\omega = \omega_{a_{1}\dots a_{p}}\bigotimes_{k = 1}^{p}d\chi^{a_{\sigma(k)}} = \omega_{a_{1}\dots a_{p}}\bigotimes_{k = 1}^{p}d\chi^{[a_{\sigma(k)}]} = \frac{1}{p!}\omega_{a_{1}\dots a_{p}}\bigwedge\limits_{k = 1}^{p}d\chi^{a_{k}}.
\end{align*}

\paragraph{The Exterior Derivative}
We define the exterior derivative of a differential form according to
\begin{align*}
	d\omega = \frac{1}{p!}\del{a_{1}}{\omega_{a_{2}\dots a_{p + 1}}}\bigwedge\limits_{k = 1}^{p + 1}d\chi^{a_{k}},
\end{align*}
which is a $p + 1$-form. This notation makes sense, as at least in the case of a $0$-form, we obtain
\begin{align*}
	d\omega = \del{a}{\omega}d\chi^{a},
\end{align*}
which is exactly the form of a dual vector. Somehow this transforms as a tensor.

\paragraph{Integration of Differential Forms}
Consider a set of $p$ tangent vectors $X_{i}$. The corresponding coordinate displacements are $\dd{\chi_{i}^{a}} = X_{i}^{a}\dd{t_{i}}$, with no sum over $i$. We would now like to compute the $p$-dimensional volume defined by the $X_{i}$ and $\dd{t_{i}}$. We expect that if any of the $X_{i}$ are linearly dependent the volume should be zero. We also expect that the volume be linear in the $X_{i}$. This implies
\begin{align*}
	\dd{V_{p}} = \omega(X_{1}, \dots, X_{p})\dd{t_{1}}\dots\dd{t_{p}}
\end{align*}
for some differential form $\omega$. We now define the integral over the $p$-volume $S$ over the $p$-form $\omega$ as
\begin{align*}
	\minteg{S}{\omega} = \integ{}{}{t_{1}}{\dots \integ{}{}{t_{p}}{\omega(\dot{\gamma}_{1},\dots, \dot{\gamma}_{p})}}.
\end{align*}
Here the $\gamma_{i}$ are the set of curves that span $S$, the dot symbolizes the derivative with respect to the individual curve parameters and the right-hand integration is performed over the appropriate set of parameter values.

\paragraph{Stokes' Theorem}
Stokes' theorem relates the integral of a differential form $d\omega$ over some subset $V$ of a manifold to an integral over \bound{V} of another differential form.
It states
\begin{align*}
	\minteg{V}{d\omega} = \oint\limits_{\bound{V}}\omega.
\end{align*}

\paragraph{Total Derivatives}
In the context of a general manifold, a total derivative is of the form $\dcov{a}{T^{aa_{1}\dots}_{b_{1}\dots}}$. Stokes' theorem states
\begin{align*}
	\minteg{V}{\dcov{a}{T^{aa_{1}\dots}_{b_{1}\dots}}} = \oint\limits_{\bound{V}}T^{aa_{1}\dots}_{b_{1}\dots}.
\end{align*}