\section{Advanced Differential Geometry}

In this part we will expand on the previously discussed concepts of differential geometry, mainly by incorporating our knowledge of tensors into it.

\paragraph{The Metric Tensor}
The metric tensor $g$ is a rank $2$ tensor. We start by defining it as $g(\vb{v}, \vb{w}) = \vb{v}\cdot\vb{w}$, but more generally the metric tensor defines the inner product.

The metric tensor is symmetric. Its components satisfy
\begin{align*}
	v_{a} = \vb{E}_{a}\cdot v^{b}\vb{E}_{b} = g(\vb{E}_{a}, \vb{E}_{b})v^{b} = g_{ab}v^{b},
\end{align*}
and likewise
\begin{align*}
	v^{a} = g^{ab}v_{b}
\end{align*}
where $\vb{v}$ is a vector. This demonstrates the capabilities of the metric to raise and lower indices.

We note that
\begin{align*}
	v_{a} = g_{ab}v^{b} = g_{ab}g^{bc}v_{c},
\end{align*}
which implies $g_{ab}g^{bc} = \kdelta{a}{c}$.

\example{The Metric in Polar Coordinates}
The contravariant components of the metric tensor, according to the definition, are
\begin{align*}
	g_{rr} = \tb{r}\cdot\tb{r} = 1,\ g_{r\phi} = g_{\phi r} = \tb{r}\cdot\tb{\phi} = 0,\ g_{\phi\phi} = \tb{\phi}\cdot\tb{\phi} = r^{2}.
\end{align*}
Likewise, the covariant components are
\begin{align*}
	g^{rr} = \db{r}\cdot\db{r} = 1,\ g_{r\phi} = g_{\phi r} = \db{r}\cdot\db{\phi} = 0,\ g_{\phi\phi} = \db{\phi}\cdot\db{\phi} = \frac{1}{r^{2}}.
\end{align*}

\paragraph{Christoffel Symbols}
When computing the derivative of a vector quantity, one must account both for the change in the quantity itself and the change in the basis vectors. We define the Christoffel symbols according to
\begin{align*}
	\del{b}{\tb{a}} = \chris{c}{b}{a}\tb{c}.
\end{align*}
These can be computed according to
\begin{align*}
	\db{c}\cdot\del{b}{\tb{a}} = \db{c}\cdot\chris{d}{b}{a}\tb{d} = \kdelta{d}{c}\chris{d}{b}{a} = \chris{c}{b}{a}.
\end{align*}
Note that
\begin{align*}
	\del{a}{\tb{b}} = \del{a}{\del{b}{\vb{r}}} = \del{b}{\del{a}{\vb{r}}} = \del{b}{\tb{a}},
\end{align*}
which implies
\begin{align*}
	\chris{c}{b}{a} = \chris{c}{a}{b}.
\end{align*}

Do the Christoffel symbols define a tensor? Someone should probably study that.

\example{Christoffel Symbols in Polar Coordinates}
To compute these, we need partial derivative of the basis vectors. We have
\begin{align*}
	\del{r}{\tb{r}} = \vb{0},\ \del{\phi}{\tb{r}} = \del{r}{\tb{\phi}} = \frac{1}{r}\tb{\phi},\ \del{\phi}{\tb{\phi}} = -r\tb{r}.
\end{align*}
We thus obtain
\begin{align*}
	\chris{a}{r}{r} = 0,\ \chris{r}{r}{\phi} = 0,\ \chris{\phi}{r}{\phi} = \frac{1}{r},\ \chris{r}{\phi}{\phi} = -r,\ \chris{\phi}{\phi}{\phi} = 0.
\end{align*}

\paragraph{Covariant Derivatives}
The partial derivate of $\vb{v} = v^{a}\tb{a}$ with respect to $\chi^{a}$ is given by
\begin{align*}
	\del{a}{\vb{v}} = \tb{b}\del{a}{v^{b}} + v^{b}\del{a}{\tb{b}} = \tb{b}\del{a}{v^{b}} + v^{b}\chris{c}{a}{b}\tb{c}.
\end{align*}
Renaming the summation indices yields
\begin{align*}
	\del{a}{\vb{v}} = \tb{b}(\del{a}{v^{b}} + v^{c}\chris{b}{a}{c}),
\end{align*}
which contains one term from the change in the coordinates and one term from the change in basis.

Realizing that derivatives of vector quantities must take both of these into account in order to transform like a tensor, we would like to define a differentiation operation that takes both of these to account when differentiating vector components. This is the covariant derivative. We define its action on contravariant vector components as
\begin{align*}
	\dcov{a}{v^{b}} = \del{a}{v^{b}} + v^{c}\chris{b}{a}{c},
\end{align*}
such that
\begin{align*}
	\del{a}{\vb{v}} = E_{b}\dcov{a}{v^{a}}.
\end{align*}
In a similar fashion we would like to define its action on covariant vector components. To do this, we use the fact that
\begin{align*}
	\del{a}{(\tb{b}\cdot\db{c})} = \del{a}{\kdelta{b}{c}} = 0.
\end{align*}
The product rule yields
\begin{align*}
	\tb{b}\cdot\del{a}{\db{c}} + \db{c}\cdot\del{a}{\tb{b}} = \tb{b}\cdot\del{a}{\db{c}} + \db{c}\cdot\chris{d}{a}{b}\tb{d} = \tb{b}\cdot\del{a}{\db{c}} + \kdelta{d}{c}\cdot\chris{d}{a}{b} = \tb{b}\cdot\del{a}{\db{c}} + \chris{c}{a}{b},
\end{align*}
which implies
\begin{align*}
	\del{a}{\db{c}} = -\chris{c}{a}{b}\db{b}.
\end{align*}
Repeating the steps above now yields
\begin{align*}
	\dcov{a}{v_{b}} = \del{a}{v_{b}} - \chris{c}{a}{b}v_{c}.
\end{align*}

\paragraph{Covariant Derivatives of Tensor Fields}

\paragraph{Christoffel Symbols and the Metric}
The derivatives of the metric tensor are given by
\begin{align*}
	\del{c}{g_{ab}} = \tb{a}\cdot\del{c}{\tb{b}} + \tb{b}\cdot\del{c}{\tb{a}} = \tb{a}\cdot\chris{d}{c}{b}\tb{d} + \tb{b}\cdot\chris{d}{c}{a}\tb{d} = \chris{d}{c}{b}g_{ad} + \chris{d}{c}{a}g_{bd}.
\end{align*}
Multiplying by $g^{ea}$ and summing over $a$ yields
\begin{align*}
	g^{ea}\del{c}{g_{ab}} = \chris{d}{c}{b}g_{ad}g^{ea} + \chris{d}{c}{a}g_{bd}g^{ea} = \chris{d}{c}{b}g_{da}g^{ae} + \chris{d}{c}{a}g_{bd}g^{ea} = \chris{e}{c}{b} + \chris{d}{c}{a}g_{bd}g^{ea}.
\end{align*}
The hope is that this can be used to obtain an expression for the Christoffel symbols. To try to do that, we will compare this to the expression obtained by switching $c$ and $b$. This expression is
\begin{align*}
	g^{ea}\del{b}{g_{ac}} = \chris{e}{b}{c} + \chris{d}{b}{a}g_{cd}g^{ea} = \chris{e}{c}{b} + \chris{d}{b}{a}g_{cd}g^{ea},
\end{align*}
yielding
\begin{align*}
	\chris{e}{c}{b} &= \frac{1}{2}\left(g^{ea}\del{c}{g_{ab}} + g^{ea}\del{b}{g_{ac}} - \chris{d}{c}{a}g_{bd}g^{ea} - \chris{d}{b}{a}g_{cd}g^{ea}\right) \\
	                &= \frac{1}{2}g^{ea}\left(\del{c}{g_{ab}} + \del{b}{g_{ac}} - \chris{d}{a}{c}g_{bd} - \chris{d}{a}{c}g_{cd}\right) \\
	                &= \frac{1}{2}g^{ea}\left(\del{c}{g_{ab}} + \del{b}{g_{ac}} - \del{a}{g_{bc}}\right).
\end{align*}

\paragraph{Curve Length}
Consider some curve parametrized by $t$, and let $\dot{\vb{\gamma}}$ denote its tangent. The curve length is given by
\begin{align*}
	\dd{s}^{2} = \dd{\vb{x}}\cdot\dd{\vb{x}} = g(\dot{\vb{\gamma}}, \dot{\vb{\gamma}})\dd{t}^{2} = g_{ab}\dot{\chi^{a}}\dot{\chi^{b}}\dd{t}^{2}.
\end{align*}
The curve length is now given by
\begin{align*}
	L = \integ{}{}{t}{\sqrt{g_{ab}\dot{\chi^{a}}\dot{\chi^{b}}}}.
\end{align*}

\paragraph{Geodesics}
A geodesic is a curve that extremises the curve length between two points. From variational calculus, it is known that such curves satisfy the Euler-Lagrange equations, and we would like a differential equation that describes such a curve. By defining $\mathcal{L} = \sqrt{g_{ab}\dot{\chi}^{a}\dot{\chi}^{b}}$, the Euler-Lagrange equations for the curve length becomes
\begin{align*}
	\del{\chi^{a}}{\mathcal{L}} - \dv{t}\del{\dot{\chi}^{a}}{\mathcal{L}} = 0.
\end{align*}
The Euler-Lagrange equation thus becomes
\begin{align*}
	&\frac{1}{2\mathcal{L}}\dot{\chi}^{b}\dot{\chi}^{c}\del{a}{g_{bc}} - \dv{t}\left(\frac{1}{2\mathcal{L}}g_{bc}(\dot{\chi}^{b}\kdelta{a}{c} + \dot{\chi}^{c}\kdelta{a}{b})\right) = 0, \\
	&\frac{1}{2\mathcal{L}}\dot{\chi}^{b}\dot{\chi}^{c}\del{a}{g_{bc}} - \dv{t}\left(\frac{1}{2\mathcal{L}}(g_{ba}\dot{\chi}^{b} + g_{ac}\dot{\chi}^{c}\right) = 0, \\
	&\frac{1}{2\mathcal{L}}\dot{\chi}^{b}\dot{\chi}^{c}\del{a}{g_{bc}} - \dv{t}\left(\frac{1}{\mathcal{L}}g_{ac}\dot{\chi}^{c}\right) = 0.
\end{align*}
Expanding the time derivative yields
\begin{align*}
	\frac{1}{2\mathcal{L}}\dot{\chi}^{b}\dot{\chi}^{c}\del{a}{g_{bc}} - \frac{1}{\mathcal{L}}\dv{t}(g_{ac}\dot{\chi}^{c}) + g_{ac}\dot{\chi}^{c}\frac{1}{\mathcal{L}^{2}}\dv{\lag}{t} = \frac{1}{2\mathcal{L}}\dot{\chi}^{b}\dot{\chi}^{c}\del{a}{g_{bc}} - \frac{1}{\lag}\dv{t}(g_{ac}\dot{\chi}^{c}) + \frac{1}{\lag}g_{ac}\dot{\chi}^{c}\dv{\ln{\lag}}{t} = 0.
\end{align*}
The curve may be reparametrized such that $\lag$ is equal to $1$ everywhere, yielding
\begin{align*}
	\frac{1}{2\mathcal{L}}\left(\dot{\chi}^{a}\dot{\chi}^{b}\del{c}{g_{ab}} - \dv{t}(2\dot{\chi}^{a}g_{ac})\right) = 0.
\end{align*}
We note that the expression in the paranthesis is the Euler-Lagrange equation for the integral of $\mathcal{L}^{2}$, a nice fact for the future. Expanding the derivative yields
\begin{align*}
	\frac{1}{\mathcal{L}}\left(\frac{1}{2}\dot{\chi}^{a}\dot{\chi}^{b}\del{c}{g_{ab}} - g_{ac}\ddot{\chi}^{a} - \dot{\chi}^{a}\dot{\chi}^{b}\del{b}{g_{ac}}\right) = 0.
\end{align*}
To remove the metric from the second derivative, we multiply by $-g^{cd}\mathcal{L}$ to obtain
\begin{align*}
	&g_{ac}g^{cd}\ddot{\chi}^{a} + \frac{1}{2}\dot{\chi}^{a}\dot{\chi}^{b}g^{cd}(2\del{b}{g_{ac}} - \del{c}{g_{ab}}) = 0, \\
	&g_{ac}g^{cd}\ddot{\chi}^{a} + \frac{1}{2}\dot{\chi}^{a}\dot{\chi}^{b}g^{cd}(\del{b}{g_{ac}} + \del{a}{g_{bc}} - \del{c}{g_{ab}}) = 0, \\
	&\ddot{\chi}^{d} + \frac{1}{2}\dot{\chi}^{a}\dot{\chi}^{b}g^{cd}(\del{b}{g_{ac}} + \del{a}{g_{bc}} - \del{c}{g_{ab}}) = 0.
\end{align*}
This is the geodesic equation. It may alternatively be written in terms of the Christoffel symbols as
\begin{align*}
	\ddot{\chi}^{d} + \chris{d}{a}{b}\dot{\chi}^{a}\dot{\chi}^{b} = 0.
\end{align*}

\paragraph{Christoffel Symbols and the Geodesic Equation}
Consider a straight line with a tangent vector of constant magnitude. In euclidean space, this is a geodesic. This curve satisfies
\begin{align*}
	\vb{0} = \dv{\dot{\vb*{\gamma}}}{t} = (\dot{\vb*{\gamma}}\cdot\grad)\dot{\vb*{\gamma}} = \dot{\chi}^{a}\del{a}{\dot{\vb*{\gamma}}} = \dot{\chi}^{a}(\dcov{a}{\dot{\chi}^{d}})\tb{d} = (\dot{\chi}^{a}\del{a}{\dot{\chi}^{d}} + \dot{\chi}^{a}\dot{\chi}^{c}\chris{d}{a}{c})\tb{d}.
\end{align*}
Comparing this to the geodesic equation yields
\begin{align*}
	\chris{d}{a}{b} = \frac{1}{2}g^{dc}(\del{b}{g_{ac}} + \del{a}{g_{cb}} - \del{c}{g_{ab}}).
\end{align*}
A better approach would have been to go through the derivation of the geodesic equation again, identifying the Christoffel symbols as you go, but I am not sure if that is what I did in the previous paragraph. In any case we have already obtained this result.

\paragraph{The Geometry of Curved Space}
In curved space, we face the restriction that there is no position vector. All vectors in curved space are instead restricted to the tangent space. It turns out that tangent vectors at a point have coordinates $\dot{\chi}^{a}$ and that the tangent vectors consist of the tangent vectors to the coordinate lines, i.e. partial derivatives.

We can also impose a metric tensor such that $\vb{v}\cdot\vb{w} = g_{ab}v^{a}w^{b}$, where the metric tensor is symmetric and positive definite.

Dual vectors can be defined as linear maps from tangent vectors to scalars, i. e. on the form
\begin{align*}
	V(\vb{w}) = V_{a}w^{a}.
\end{align*}
In particular, the dual vector $\dd{f}$ can be defined as
\begin{align*}
	\dd{f}(\vb{v}) = v^{a}\del{a}{f} = \dv{f}{t}
\end{align*}
along a curve with $\vb{v}$ as a tangent. A basis for the space of dual vectors is $e^{a} = \dd{\chi^{a}}$. The tangent and dual spaces, if a metric exists, are related by $v_{a} = g_{ab}v^{b}$.

Curve lengths are defined and computed as before. By defining geodesics as curves that extremize path length, this gives a set of Christoffel symbols and therefore a covariant derivative and a sense of what it means for a vector to change along a curve.